Workflow Part II: Inverse root depth modeling and post-processing

### 2021-07-02 Readme.Rmd
Added LANL C #

---
title: "Workflow Part II: Inverse root depth modeling and post-processing"
author: "Rutuja Chitra-Tarak"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
  md_document:
subtitle: Hydraulically-vulnerable trees survive on deep-water access during droughts
  in a tropical forest
---

@@

© 2021. Triad National Security, LLC. All rights reserved.

>>>>

---
title: "Workflow Part II: Inverse root depth modeling and post-processing"
author: "Rutuja Chitra-Tarak"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  md_document:
  html_document:
    df_print: paged
  word_document: default
  pdf_document: default
subtitle: Hydraulically-vulnerable trees survive on deep-water access during droughts
  in a tropical forest
---

@@

© 2021. Triad National Security, LLC. All rights reserved. LANL C20130.
